Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-10-16 TACAS2018/paper.tex
more comments

Let us first consider the effect of the quantization errors. 
Within the controller, state values are manipulated at low precision,
alongside the vector multiplication $\mat{K}\vec{x}$.
Furthermore, 
the quantizers for the DAC and the ADC introduce truncation errors
which we denote by the effect of the functions $\mathcal{F}_{\langle D \rangle}$
and $\mathcal{F}_{\langle A \rangle}$ respectively. Finally, let us call $\vec{\nu}_e$ the
error caused by the FWL effects on the observer (\emph{i.e} the numerical errors 
in the calculations as opposed to the estimation error).
The inputs are computed using the following equation: 
%
\begin{align}
u_{k}&=\mathcal{F}_{\langle D \rangle}\left(-\mat{K}_{\langle C \rangle}\cdot\left(\mathcal{F}_{\langle C \rangle}\left(\mathcal{F}_{\langle A \rangle}(\vec{x}_{k})\right)\right) +\vec{\nu}_e\right)
\label{eq:uk}
\end{align}

@@

%-------------------------------
\section{Specification of control systems properties} 
\label{sec:specification}
%-------------------------------

@@

where $\mat{G}$ is a matrix of template directions taken as row vectors, and $\vec{h}$ is an upper
bound for the set in the corresponding row direction.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Verification of a Controllable Observed System}\label{sec:cof_verification}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

Thus far we looked at checking stability
%have presented a verification procedure for
of a continuous plant in discretized time domain (i.e., the range of the quatizers is still
$\mathbb{R}$) \todo{do you mean that we only considered time domains discretization until now and
now we look at value domain discretization as well?}.  The next step we must realize is that the controller and the
observer exist in a digital program, hence their domain is
$\mathbb{R}_{\langle C \rangle}$.  This has two separate effects on the
model.  If we recall Equation~\eqref{eq:observer_LTI}, the matrices of the observer
and the controller are not necessarily those of the plant.  In fact we have
$\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$, ${\mat{A}_d}_{\langle C
\rangle},{\mat{B}_d}_{\langle C \rangle},{\mat{C}_d}_{\langle C \rangle},
\mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \in
\mathbb{R}_{\langle C \rangle}^*$ where $*$ represents the appropriate
dimension for each matrix.  Unfortunately this means that although combined
matrices such as $\mat{A}_t$ are in the reals, they suffer from the fixed
word restrictions in their composing matrices.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Safety of a Digitally Observed System}\label{sec:cof_safety}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

%% Now that we have established convergence, we may examine the safety
%% specification of the state space.
In the case of SISO systems, the safety specification is
given by a range of the input and a range of the output which are considered
safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in
[\underline{y}\ \ \overline{y}]$)
\todo{I think the safety specification is generally on the states of the system.}.
Whilst there are other properties we may
include in the verification, we will solely focus on these for simplicity of
the explanation.  We assume that we do not want saturation in our
system, hence the control loop has only one mode.
%We have also identified the quantization noise as a bounded non-deterministic input.
First we must
translate the safety specification into the statespace.  Replacing on the
second part of equation \eqref{eq:observer_LTI_cf} we obtain
%
\begin{equation}
\phi_{safety} := \underline{y}<\mat{C}\vec{x}_k<\overline{y}, \forall k \geq 0
\label{eq:of_bounds}
\end{equation}
%
%Note that we use the bounds of the input after the transformation by $\mat{B}$ since the matrix may reverse the bounds. 
%
%We evaluate the progression of the system over time by calculating
%$\vec{x}_k$ to validate against this specification.  For this step we require
%an initial set $\vec{x}_0$ from which the system progresses.  Obviously, this set
%must satisfy the specification, otherwise the system will be
%unsafe to begin with.  For efficiency purposes, the inequality in \eqref{eq:of_bounds} is transformed into reachable form using $\mat{T}_c, \mat{T}_o$ which reduces the complexity from $\mathcal{O}(p^2)$ to $\mathcal{O}(p)$.

@@

\todo{this descrition does not mention two synthesis phases, which we should
focus on more.}

@@

The CEGIS loop for this approach 
\todo{the description here is incomplete (stops at phase 4).}

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Numerical representation and soundness} 
\label{sec:numeric_rep}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

>>>>

Let us first consider the effect of the quantization errors. 
Within the controller, state values are manipulated at low precision.
%alongside the vector multiplication $\mat{K}\vec{x}$.
Furthermore, the quantizers for the DAC and the ADC introduce truncation errors
which we denote by the effect of the functions $\mathcal{F}_{\langle D \rangle}$
and $\mathcal{F}_{\langle A \rangle}$, respectively. Finally, let us call $\vec{\nu}_e$ the
error caused by the FWL effects on the observer
\todo{the observer was not defined..}
(\emph{i.e} the numerical errors 
in the calculations as opposed to the estimation error).
The inputs are computed using the following equation: 
%
\begin{align}
u_{k}&=\mathcal{F}_{\langle D \rangle}\left(-\mat{K}_{\langle C \rangle}\cdot\left(\mathcal{F}_{\langle C \rangle}\left(\mathcal{F}_{\langle A \rangle}(\vec{x}_{k})\right)\right) +\vec{\nu}_e\right)
\label{eq:uk}
\end{align}

@@

%-------------------------------
\section{Specification of control systems properties} 
\label{sec:specification}
%-------------------------------
\todo{all this section needs to be merged with the next one and only
discussed for an observed model.}

@@

where $\mat{G}$ is a matrix of template directions taken as row vectors \todo{unclear to me}, and $\vec{h}$ is an upper
bound for the set in the corresponding row direction.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Verification of a Controllable Observed System}\label{sec:cof_verification}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\todo{the observer dynamics?}

@@

Thus far we looked at checking stability
%have presented a verification procedure for
of a continuous plant in discretized time domain (i.e., the range of the quatizers is still
$\mathbb{R}$).  The next step we must realize is that the controller and the
observer exist in a digital program, hence their domain is
$\mathbb{R}_{\langle C \rangle}$.  This has two separate effects on the
model.  If we recall Equation~\eqref{eq:observer_LTI}, the matrices of the observer
and the controller are not necessarily those of the plant.  In fact we have
$\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$, ${\mat{A}_d}_{\langle C
\rangle},{\mat{B}_d}_{\langle C \rangle},{\mat{C}_d}_{\langle C \rangle},
\mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \in
\mathbb{R}_{\langle C \rangle}^*$ where $*$ represents the appropriate
dimension for each matrix.  Unfortunately this means that although combined
matrices such as $\mat{A}_t$ are in the reals, they suffer from the fixed
word restrictions in their composing matrices.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Safety of a Digitally Observed System}\label{sec:cof_safety}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\todo{FWL effects here?}

%% Now that we have established convergence, we may examine the safety
%% specification of the state space.
In the case of SISO systems, the safety specification is
given by a range of the input and a range of the output which are considered
safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in
[\underline{y}\ \ \overline{y}]$)
Whilst there are other properties we may
include in the verification, we will solely focus on these for simplicity of
the explanation.  We assume that we do not want saturation in our
system, hence the control loop has only one mode.
%We have also identified the quantization noise as a bounded non-deterministic input.
First we must
translate the safety specification into the statespace.  Replacing on the
second part of equation \eqref{eq:observer_LTI_cf} we obtain
%
\begin{equation}
\phi_{safety} := \underline{y}<\mat{C}\vec{x}_k<\overline{y}, \forall k \geq 0
\label{eq:of_bounds}
\end{equation}
\todo{Using \eqref{eq:observer_LTI_cf} doesn't result in this.}
%
\todo{transient response?}
%
%Note that we use the bounds of the input after the transformation by $\mat{B}$ since the matrix may reverse the bounds. 
%
%We evaluate the progression of the system over time by calculating
%$\vec{x}_k$ to validate against this specification.  For this step we require
%an initial set $\vec{x}_0$ from which the system progresses.  Obviously, this set
%must satisfy the specification, otherwise the system will be
%unsafe to begin with.  For efficiency purposes, the inequality in \eqref{eq:of_bounds} is transformed into reachable form using $\mat{T}_c, \mat{T}_o$ which reduces the complexity from $\mathcal{O}(p^2)$ to $\mathcal{O}(p)$.

@@

\todo{this description does not mention two synthesis phases, which we should
focus on more.}

@@

The CEGIS loop for this approach is described next.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Numerical representation} 
\label{sec:numeric_rep}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

\todo{preliminaries should also contain the observer model.}
\todo{why is sec 4 not considering the observer model or a system with output?}
\todo{sec 6 needs to be merged into 7.}
\todo{transient response for an observed model?}
